The paper on blockchain front-running

### 2018-09-24 frontrunning/Latex/sections/paper.tex
took a long time to get here, but now into the TOP 25 section :+1:

% !TEX root = ../main.tex
%______________________________________________________________%
\section{Introduction}

\label{sec:intro}

% @J : intro needs lots of love.
% Jeremy: Will work on this very last, once I know what the paper is actually about :)

@@

The mechanics of frontrunning works on all DApps but front-running is not beneficial on all DApps; it depends on its internal logic as well as any mitigations it might implement. This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps). We study DApps from each category of the top 25 most active\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} to assess their vulnerability to front-running attacks. We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day. Proposals to eliminate or mitigate frontrunning from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them here.

%The concept of  \emph{front-running} is decades old starting with early financial markets. Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change. Clearly, in such scenarios front-running was possible yet not detectable as a damaging activity. However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, a new form of front-running is feasible through high-speed networks. Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}. Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis. Surprisingly, there was no ICO (initial coin offering) included in the top 25 DApps list by the time we fetched the data from the website. We believe the reason is that the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over. Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 DApps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}

\textblue{[tk]} As a preview, in Section~\ref{sec:frontrunningExchanges}), we examine Bancor~\cite{hertzog2017bancor}, a decentralized exchange that operates similar to traditional stock markets and is likewise vulnerable to front-running. Domain name frontrunning occurs when a user uses a domain registrar to inquire if a domain is available for purchase, and the query triggers the registrar to purchase the domain in anticipation that it can sell it to the user. In Section~\ref{sec:ens}, we examine decentralized namespaces like Ethereum Name Service and academic works like Ghazal~\cite{moosavighazal} where relaying nodes and miners see Alice's attempt to purchase a domain name before it is finalized in a block. A front-running node might try to supersede her transaction. In Section~\ref{sec:ICOsfrontrunning}, we look at Initial Coin Offerings (ICOs). After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}. We show empirical evidence of a miner purchasing tokens ahead of other users.

%Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions. Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them. We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues arising from these new models. Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial. Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] loosely to talk about any transaction manipulation with the intention of getting other transactions in before the original transaction takes place. In this paper, our focus is to have a complete overview of front-running on the blockchain while analyzing Bancor issues. While looking at the possibility of front-running on other applications, we found interesting case studies that affect most of the top 25 decentral applications on Ethereum blockchain.

%______________________________________________________________%
\section{Preliminaries \& Related Work}

@@

\emph{Front-running} is a course of action where someone benefits from early access to market information about upcoming transactions and trades, typically because of a privileged position along the transmission of this information. The problem can occur in both financial and non-financial systems. In traditional stock exchanges, floor traders might overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large sale temporarily reduces supply of the stock. Brokers might also frontrun their own client's orders by purchasing stock for themselves between receiving the instruction to purchase from the client and actually executing the purchase (similar techniques can be used for large sell orders). Front-running is unethical and illegal in jurisdictions with mature securities regulation.

% Jeremy: I don't real;y understand the below so dropping if no one protests. 
%The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}.

\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
%As traditional front-running has been the subject of discussion for decades, there are many works of literature on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first observed on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by Securities Exchange Commission \textit{(SEC)} in 1977 as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}''

% More to read:  SECURITIES AND EXCHANGE COMMISSION Release No. 34-67079. pdf included in Related_Documents
% https://www.sec.gov/about/annual_report/1988.pdf

@@

% everything that has a lineup, someone can jump in the line and front-run

In one sense, blockchain technology (which was introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that would participate in a transaction. However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions. Any network participant that runs a full node on the blockchain is able to obtain proposed transactions before they are added to the blockchain and miners are free in the transactions they select for inclusion in their attempted blocks. This can leave blockchain applications vulnerable to front-running, as we will see through the several case studies detailed in this paper.

%____________________________________________________________________

@@

Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running.
%As mentioned in section~\ref{sec:What is front-running?}, the information leakage results in the entire system to be vulnerable to the front-running.  %In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}. They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient. Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. In order to mitigate this issue they proposed \textit{Submarine Commitments} which extend commit and reveal; we discuss them further in Section~\ref{submarineCommits}.

@@

%\textblue{Equate front-running to a rushing adversary in the crypto literature and cite the fact that UC models of blockchains capture front-running attacks: cite Bitcoin Backbone paper and Hawk paper in particular.}

%___________________________________________________________%

\section{Who are Blockchain Front-runners?} %\section{On Blockchain Front-running}
\label{sec:who can front-run?}

%Blockchain, as a secure ledger, gives the impression of an ultimate secure platform for decentral applications and one might not consider implementing the application with security in mind. In general, all the network participants have the ability to front-run specific transactions that are sent to the network. Also, miners can include any transactions they like into the block they attempt to mine. Thus, they possess special power in terms of front-running as opposed to other users of the network. In the following, we discuss and compare the two groups of blockchain potential front-runners.

\paragraph{Full Nodes.}
Any regular (miner or non-miner) the user can front-run other transactions in the network. For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network. Doing so, they are able to listen to the network and monitor all transactions that are broadcast. On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textit{gas}~\cite{AccountT67:online}. The price that users pay for transactions, \textit{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine. Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine. Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price, see figure~\ref{fig:RegularFrontrunning}. For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction. By doing so, he achieves a better rate from the buyer. Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants. The probability of success in such attach can be increased by flooding the network by transactions with higher than average gasPrice.

@@

\paragraph{Miners.} \label{minersfrontrunning}
Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textbf{transaction reordering} attack. For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase. So the dishonest miner can step in front of this transaction and place his own buy order ahead. He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction in the block he mines. Doing so, he would receive a better rate than other network users, and afterward can sell the assets he has bought and gained a price advantage. It should be noted that miners can only front-run transactions within the blocks they happen to mine. They could do this also by not broadcasting their own transactions to the network before including it in the block, this makes the miners be less noticeable to the network when front-running.
Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when the user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own transaction to fill that order in front of the cancellation transaction --transaction reordering--, potentially profiting from the order. He can also include the canceled transaction in the block to collect the full gas limit used by the cancel transaction~\cite{CostofDecentralization:online}, see figure~\ref{fig:MinerFrontrunning}. Front-running can also occur in non-financial smart contracts. As an example, a smart contract which adds all the participants to a party invite list could only be closed by the smart contract owner. In this case, when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines. This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.

@@

\section{Cases of Front-running in DApps}

As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \texttt{DAppradar.com}\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} in the first week of September 2018. We then categorize these applications into 4 principal groups of decentral applications (see Table~\ref{tab:top25DApps}). In this section, we take a deep look into one or two decentral applications from each category and pinpoint the technical details of front-running issue on each case. Although no ICOs were spotted on the list at the time it was retrieved, we will thoroughly discuss our analysis of how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).

\input{setup/table}

%______________________________________________________________%
\subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}

%Tragedy of the commons

Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, is the closest implementation to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website). Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs. Similarly 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and are not prone to cheating. One main issue with these designs is the \textit{cancellation grief}. Although the order books are not in the smart contract, in order to prevent denial of service attacks, the user needs to send a transaction to cancel her order. In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is canceled. As mentioned in ~\ref{minersfrontrunning}, miners are in a better position to perform such an attack.

Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that is always available to users. ERC20 is the interface standard for implementing tokens on top of Ethereum~\cite{erc20}. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
Implemented on the Ethereum blockchain, when transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them. Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block. This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}. Researchers have shown and implemented a proof of concept code to front-run Banco as a regular non-miner user~\cite{NewTab13:online}.

Front-running can also occur within non-financial blockchain applications such as naming systems. Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduced the single point of failures to the entire web. Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names. Although sealed auction method is used in ENS implementation, the normal workflow uses \textit{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid. By doing so the front-runner invalidates the original bid and hence registers the domain name himself. Ghazal is another Ethereum-based naming system that allows users to register \texttt{.ghazal} domain names and bind certificates to those names~\cite{moosavighazal}.  As Ghazal is using a registration method in plain text, it is susceptible to front-running. 
Note that front-running domain names has been a subject of discussion outside the context of blockchian applications before~\cite{sac022en33:online}. Domain name registrars can steal available domain names upon seeing a query from an interested user for the availability of the domain. In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.
%______________________________________________________________%
\subsection{Crypto-Collectibles Games.}

@@

@@

@@

>>>>

% !TEX root = ../main.tex

\section{Introduction} \label{sec:intro}

@@

The mechanics of frontrunning works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or  as any mitigations it might implement. Therefore DApps need to be studied individually or in categories. This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectables (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service). We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day. After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}. We show empirical evidence of a miner purchasing tokens ahead of other users in Status.im. Finally, proposals to eliminate or mitigate frontrunning from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them the last section.

% = = = = = = = = = = = = = = = = = = = = = = = = = = %
% = = = Preliminaries
% = = = = = = = = = = = = = = = = = = = = = = = = = = %

\section{Preliminaries \& Related Work}

@@

\emph{Front-running} is a course of action where someone benefits from early access to market information about upcoming transactions and trades, typically because of a privileged position along the transmission of this information. The problem can occur in both financial and non-financial systems. In traditional stock exchanges, floor traders might overhear a broker's negotiation with her client over a large purchase, and literally race the broker to buy first, potentially profiting when the large sale temporarily reduces supply of the stock. A malicious broker might also front-run their own client's orders by purchasing stock for themselves between receiving the instruction to purchase from the client and actually executing the purchase (similar techniques can be used for large sell orders). Front-running is unethical and illegal in jurisdictions with mature securities regulation.

Cases of front-running are sometimes difficult to distinguish from related concepts like insider trading and arbitrage. In front-running, a person sees a concrete transaction that is set to execute and reacts to it before it actually executes. If the person instead has access to more general privileged information that might predict future transactions, but is not reacting at the actual pending trades, we would classify this activity as insider trading. If the person reacts after the trade is executed, or information is made public, and profits from being the fastest to react, this is considered arbitrage and is both legal and encouraged because it helps markets integrate new information into prices quickly.

\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
Front-running was first observed on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by Securities Exchange Commission \textit{(SEC)} in 1977 as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}''

@@

In one sense, blockchain technology (which was introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that would participate in a transaction. However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions that can act as front-runners. Any user monitoring blockchain network transactions (\eg running a full node) can see a unconfirmed transactions and broadcast a reactionary transaction that might be confirmed ahead of the original transaction ...

 that is well-connected front-run other transactions in the network. For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network. Doing so, they are able to listen to the network and monitor all transactions that are broadcast. On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textit{gas}~\cite{AccountT67:online}. The price that users pay for transactions, \textit{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine. Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine. Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price. Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textbf{transaction reordering} attack.

@@

Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}.They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running. Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}. They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient. Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. In order to mitigate this issue they proposed \textit{Submarine Commitments} which extend commit and reveal; we discuss them further in Section~\ref{submarineCommits}.

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = %
% = = = TOP 25
% = = = = = = = = = = = = = = = = = = = = = = = = = = %

\section{Cases of Front-running in DApps}  
\input{setup/table}

To find example DApps to study, we use the top 25 DApps based on recent user activity from \texttt{DAppradar.com} and sampled it in in the first week of September 2018.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} User activity is admittedly an imperfect metric for finding the `most significant' DApps: significant DApps might be lower volume overall or for extended periods of time (\eg ICOs, which we remedy by studying independently in Section~\ref{sec:ICOsfrontrunning}). However user activity is arguably the best objective criteria for which data is readily available, the list captures our intuition about which DApps are significant, and it is at least better than an ad hoc approach. Using the dataset, we categorized the top 25 applications into 4 principal use cases. The details are given in Table~\ref{tab:top25DApps}.

\subsection{Markets and Exchanges.} \label{sec:frontrunningExchanges}

%Tragedy of the commons
The first category of DApp in Table~\ref{tab:top25DApps} is exchanges. 
Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, is the closest implementation to decentral exchanges, however their order books are stored on a central server they control and shown on their user interface (website). Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs. Similarly 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and are not prone to cheating. One main issue with these designs is the \textit{cancellation grief}. Although the order books are not in the smart contract, in order to prevent denial of service attacks, the user needs to send a transaction to cancel her order. In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is canceled. As mentioned in ~\ref{minersfrontrunning}, miners are in a better position to perform such an attack.

@@

@@

see figure~\ref{fig:RegularFrontrunning}. For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction. By doing so, he achieves a better rate from the buyer. Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants. The probability of success in such attach can be increased by flooding the network by transactions with higher than average gasPrice.

For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase. So the dishonest miner can step in front of this transaction and place his own buy order ahead. He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction in the block he mines. Doing so, he would receive a better rate than other network users, and afterward can sell the assets he has bought and gained a price advantage. It should be noted that miners can only front-run transactions within the blocks they happen to mine. They could do this also by not broadcasting their own transactions to the network before including it in the block, this makes the miners be less noticeable to the network when front-running.

Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when the user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own transaction to fill that order in front of the cancellation transaction --transaction reordering--, potentially profiting from the order. He can also include the canceled transaction in the block to collect the full gas limit used by the cancel transaction~\cite{CostofDecentralization:online}, see figure~\ref{fig:MinerFrontrunning}. Front-running can also occur in non-financial smart contracts. As an example, a smart contract which adds all the participants to a party invite list could only be closed by the smart contract owner. In this case, when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines. This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.

Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that is always available to users. ERC20 is the interface standard for implementing tokens on top of Ethereum~\cite{erc20}. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
Implemented on the Ethereum blockchain, when transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them. Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block. This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}. Researchers have shown and implemented a proof of concept code to front-run Bancor as a regular non-miner user~\cite{NewTab13:online}.

%______________________________________________________________%
\subsection{Crypto-Collectibles Games.}

The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables.

@@

The third category of DApp in Table~\ref{tab:top25DApps} is gambling services.

@@

The final category of DApp in Table~\ref{tab:top25DApps} is name services.

Front-running can also occur within non-financial blockchain applications such as naming systems. Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduced the single point of failures to the entire web. Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names. Although sealed auction method is used in ENS implementation, the normal workflow uses \textit{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid. By doing so the front-runner invalidates the original bid and hence registers the domain name himself. Ghazal is another Ethereum-based naming system that allows users to register \texttt{.ghazal} domain names and bind certificates to those names~\cite{moosavighazal}.  As Ghazal is using a registration method in plain text, it is susceptible to front-running. 
Note that front-running domain names has been a subject of discussion outside the context of blockchian applications before~\cite{sac022en33:online}. Domain name registrars can steal available domain names upon seeing a query from an interested user for the availability of the domain. In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.

%% = = = = = = = = = = = = = = = = = = = = = = = = = = %
% = = = ICOs
% = = = = = = = = = = = = = = = = = = = = = = = = = = %%

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = %
% = = = Mitigations
% = = = = = = = = = = = = = = = = = = = = = = = = = = %
